---
title: Statistical Analysis of Behavioral Data
subtitle: Data Driven Approach
date: "`r format(Sys.time(), '%d %B, %Y')`"
author: Ahmad Ehyaei
institute: Max-Planck Institute
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [src/styles/template.css, src/styles/environments.css]
    nature:
      highlightStyle: github
      highlightLines: true
      ratio: "16:10" 
      slideNumberFormat: "%current% / %total%"
      navigation:
        scroll: false
---

```{r setup, include=FALSE}
source("manuscript/global.R")
```


class: inverse, center, middle

# XARINGAN

---
# Section Design

This is simple an R Markdown document to show MPIThemes features.
use `#` sign to define chapter.
For definition sub chapter add `##` to first line and add name of sub chapter.

---
# Code Embedding

```{r cars}
summary(cars)
```

We can run inline R code `2^10=` `r 2^10`

---
# Markdown

In RMarkdown we can use markdown syntax, such as unordered list items

- item
- item
    - more item

Or use block quotes are written after `>`, e.g.,

> To be, or not to be, that is the question!

---
# Latex Formula

We can easily write math expressions by latex syntax. 
Inline LateX equations can be written in a pair of dollar signs
$$f\left(k\right)=\binom{n}{k}p^k\left(1-p\right)^{n-k}$$

---
# Plot

```{r scatterPlot1}
ggplot(iris, aes(Sepal.Length, Petal.Length)) + 
  geom_point(aes(color=Species, size=Sepal.Width),alpha = 0.5) +
  geom_smooth(aes(col=Species), method="lm", se=F)
```

---
# Plot with Code

By using ggplot package, we can  

.pull-left[
.code60[
```{r scatterPlot2, echo=TRUE,eval=FALSE}
ggplot(
  iris, 
  aes(Sepal.Length, Petal.Length)
  ) + 
  labs(
    subtitle="Sepal Length vs Petal Length",
    title="Bubble chart") + 
  geom_point(
    aes(color=Species, size=Sepal.Width),
    alpha = 0.5
    ) +
  geom_smooth(
    aes(col=Species), 
    method="lm", 
    se=F
    )
```
]
]

.pull-right[
```{r scatterPlot3, echo=FALSE,fig.height=6}
ggplot(iris, 
       aes(Sepal.Length, Petal.Length)) + 
  labs(subtitle="Sepal Length vs Petal Length",
       title="Bubble chart") + 
  geom_point(aes(color=Species, size=Sepal.Width),alpha = 0.5) +
  geom_smooth(aes(col=Species), method="lm", se=F)
```
]

---
# Block Environments

.rmdWarning[
Lorem Ipsum is simply dummy text of the printing and typesetting industry. 
]

.rmdtip[
Lorem Ipsum is simply dummy text of the printing and typesetting industry. 
]

.Theorem[
This is a theorem about right triangles and can be summarised in the next 
equation 
$$x^2 + y^2 = z^2 $$
]

---
class: inverse, center, middle

# Thank You for Attention
