---
title: Analysis of Behavioral Task
subtitle: Data Driven Report
author: Ahmad Ehyaei
date: "`r format(Sys.Date(), '%d %B %Y')`"
output: 
  powerpoint_presentation:
    reference_doc: src/styles/template.pptx
---

```{r setup, include=FALSE}
source("manuscript/global.R")
```

# PowerPoint

## Start Presentation

This is simple an R Markdown document to show MPIThemes features.
use `#` sign to define chapter.
For definition subsection add `##` to first line and add name of sub chapter.

## Code Embedding

```{r cars,echo=TRUE}
summary(cars)
```

We can run inline R code `2^10 = ` `r 2^10`

## Markdown

In RMarkdown we can use markdown syntax, such as unordered list items

- item
- item
    - more item

Or use block quotes are written after `>`, e.g.,

> To be, or not to be, that is the question!

## Math Formula

We can easily write math expressions by latex syntax. 
Inline LateX equations can be written in a pair of dollar signs
$$f\left(k\right)=\binom{n}{k}p^k\left(1-p\right)^{n-k}$$

## Plot

```{r scatterPlot, echo=FALSE}
ggplot(iris, aes(Sepal.Length, Petal.Length)) + 
  labs(subtitle="Sepal Length vs Petal Length",
       title="Bubble chart") + 
  geom_point(aes(color=Species, size=Sepal.Width),alpha = 0.5) +
  geom_smooth(aes(col=Species), method="lm", se=F)
```
