---
title: "GGPLOT2 Themes & Palettes"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(MPIThemes)
library(ggplot2)
if (!require("dplyr")) install.packages("dplyr")
library(dplyr)
```


This package includes several ggplot themes and palettes for creating plots with
MPI custom design.

## Color Palette

This palette was inspired by the CD manual (available \href{https://docplayer.org/2328711-Max-planck-institut-das-erscheinungsbild-der-max-planck-gesellschaft-4-ueberarbeitete-auflage.html}{here} )
of the Max Planck Society.

Max-Planck institute has a standard style for document design. You can find CD manual 
\href{https://docplayer.org/2328711-Max-planck-institut-das-erscheinungsbild-der-max-planck-gesellschaft-4-ueberarbeitete-auflage.html}{here}. The two main colors in this document are green (Pantone 328) and gray (Pantone 427).
The Pantone color system is a standardized color matching system, which is widely used. 
Below we can see traditional two main colors in Max-Planck society.

```{r max_planck_colors,crop = TRUE,out.width="50%"}
scales::show_col(c("#116656","#DDDED6"))
```

To find a color palette,  Some colors are chosen from the Pantone list that is different from the two main colors.  Color selection is a process in progress.

```{r mpithemes_palette,crop = TRUE,out.width="50%"}
scales::show_col(palette_mpi(),ncol = 3)
```

There are some examples here.

```{r mpithemes_colors,echo=FALSE,out.width="100%"}
library(ggplot2)

k = 9
# Define a set of figures to play with using the Iris dataset
df1 = data.frame(x = rnorm(100*k),y = rnorm(100*k),type = letters[1:k])
point_plot <- ggplot(df1, aes(x=jitter(x), y=jitter(y), col=type)) + 
  geom_point() + 
  theme_void()+
  scale_color_mpi()+
  labs(x= NULL,y = NULL)+
  theme(legend.position = "none")


df2 = data.frame(y = abs(rnorm(k))+2,x = letters[1:k])

bar_plot <- ggplot(df2, aes(x=x, y=y, fill=x)) + 
  geom_bar(stat="identity") + 
  theme_void()+
  scale_fill_mpi()+
  labs(x= NULL,y = NULL)+
  theme(legend.position = "none")
df1$x = df1$x+as.integer(as.factor(df1$type))

density_plot <- ggplot(df1, aes(x=x, fill=type)) + 
  geom_density(alpha = 0.8,color = "transparent") +
  theme_void()+
  scale_fill_mpi()+
    labs(x= NULL,y = NULL)+
  theme(legend.position = "none")

box_plot <- ggplot(df1, aes(x=x, fill=type)) + 
  geom_boxplot(alpha = 0.8,size = 0.1) +
  theme_void()+
  scale_fill_mpi()+
    labs(x= NULL,y = NULL)+
  theme(legend.position = "none")

# Display this figure:
gridExtra::grid.arrange(point_plot,bar_plot,density_plot,box_plot,ncol = 2)

```

## Theme

```{r mpithemes_theme_scientific,eval=TRUE,echo=FALSE}
k = 3
data.frame(x = rnorm(100*k),y = rnorm(100*k),type = letters[1:k]) %>% 
ggplot(aes(x=jitter(x), y=jitter(y), col=type)) + 
  geom_point() + 
  labs(x= "Width",y = "Height")+
  theme_scientific()+
  scale_color_mpi()
```


```{r,include=FALSE}
fig.path = list.files("../../docs/articles/articles/02_ggplot2_themes_files/figure-html",full.names = T)
for(im in fig.path){
  knitr::plot_crop(im)
}
```

