---
title: "Use Python To Generate PDF Report"
---



```{r,include=FALSE}
source("../../examples/python_pdf_report/manuscript/global.R")
if (!require("reticulate")) install.packages("reticulate")
library(reticulate)
```

# Reticulate

The `MPIThems` templates aren't just for R users, Python programmers may also enjoy them
by [reticulate](https://rstudio.github.io/reticulate/index.html) package.
The `reticulate` brings a Python engine for R Markdown and allowing  simple interchange between Python and R chunks.
For install `reticulte` use cran repository as below:

```{r,eval=FALSE,echo=TRUE}
install.packages("reticulate")
```

## Choose Python version

The first step to running Python code is to choose the Python engine or environment. There are two ways to choose a Python environment:

1. By default, `reticulate` uses the system Python found on your OS. To find the path, run the R command `Sys.which("python")` on the console.
Alternatively, to use your installed Python, add your Python path with the command `use_python()` to set the default engine.

```{r,eval=FALSE,echo=TRUE}
library(reticulate)
use_python("/usr/local/bin/python")
```

2. If you have an `Anaconda` or `Miniconda`, you may use the use `use_condaenv()` or use `use_virtualenv()` to run Python code in any of these environments.

```{r,eval=FALSE,echo=TRUE}
use_condaenv("Python3.8", required = TRUE) # Name of environment
```

The `r-reticulate` `Conda` environment will be created when the `reticulate` package is installed.
To see the list of your `Conda` environment, run command `conda list env` in bash or `retculate::conda_list()` R command.
Run the `py_config()` command to ensure that `reticulate` is utilizing your updated `Conda` env.

## Install Python Package

The `reticulate` env has minimal Python packages. In order to install a new package, use `py_install()` command. The packages will be installed by default in `r-reticulate` env.
For more information you can see `reticulate`'s vignette [Installing Python Packages](https://rstudio.github.io/reticulate/articles/python_packages.html)

```{r,eval=FALSE,echo=TRUE}
py_install("pandas")
```

## Check Python working

To ensure that everything is working properly, try writing a basic Python code in RMarkdown. 
Set the Python command in the Python chunk `{python}` for this.

```
'''{python}
import numpy as np
import pandas as pd
np.arange(1, 10)
'''
```

```{python,eval=TRUE, echo=FALSE}
import numpy as np
import pandas as pd
np.arange(1, 10)
```

For the convenience of Python coding in RMarkdown, it is recommended that you create a shortcut to generate the python chunks.
To create shortcut go to `Tools -> Modify Keyboard Shortcuts` and search `python` word to find `Insert Chunk Python`. 
Then click on it and set a suitable shortcut for it. `Ctrl + Alt + P` sounds a good option. 

In the following example, we use the `pandas` package to construct a data frame and `matplolib` to plot the data.

```{python matplotlib,echo=TRUE,fig.height=2}
import matplotlib as plt
df = pd.DataFrame(data = {"x":np.arange(1,10,.01)})
df = df.assign(y=np.cos(df["x"]))
df.plot(x="x", y = "y", title = "Simple Matplotlib Plot in RMarkdown")
```

Fortunately, Package `ggplot2` has also been implemented for Python. 
Below is an example of drawing a ggplot in Python.

```{python ggplot,echo=TRUE,fig.height=2}
from plotnine.data import economics
from plotnine import ggplot, aes, geom_line
ggplot(df) + aes(x="x", y="y") + geom_line()
```

## Calling Python from R

All objects created within Python chunks are available to R by calling the `py$object`. 
In the below example, we plot the previously Python-produced data with ggplot in R.


```{r ggplot2R,echo=T}
ggplot(py$df, aes(x=x, y=y)) + 
  geom_line()
```

