---
title: "Statistical analysis of behavioral data "
date: "`r format(Sys.time(), '%d %B, %Y')`"
author: [Ahmad Ehyaei, Sara Ershadmanesh]
affiliation: Max Planck Institute for Biological Cybernetics 
location: Tübingen
titlepage: true
toc: true
content-has-page: true
titlepage-color: 009EE2
titlepage-text-color: FFFFFF
titlepage-rule-color: FFFFFF
title-vjust: 150
logo-secondary: src/icon/MPILogoWhite.eps
output:
  MPIThemes::latex_report
...

```{r,include=FALSE}
source("manuscript/global.R")
```

# RMarkdown+Latex

This is simple an R Markdown document to show MPIThemes features.
use `#` sign to define chapter.
For definition sub chapter add `##` to first line and add name of sub chapter.

## Code Embedding

```{r cars}
summary(cars)
```

We can run inline R code `2^10=` `r 2^10`

## Markdown

In RMarkdown we can use markdown syntax, such as unordered list items

- item
- item
    - more item

Or use block quotes are written after `>`, e.g.,

> To be, or not to be, that is the question!

## Latex

We can easily write math expressions by latex syntax. 
Inline LateX equations can be written in a pair of dollar signs
$$f\left(k\right)=\binom{n}{k}p^k\left(1-p\right)^{n-k}$$

## plot

By using ggplot package, we can  

```{r scatterPlot, echo=TRUE}
ggplot(iris, aes(Sepal.Length, Petal.Length)) + 
  labs(subtitle="Iris Data: Sepal Length vs Petal Length",
       title="Bubble chart") + 
  geom_jitter(aes(col=Species, size=Sepal.Width)) + 
  geom_smooth(aes(col=Species), method="lm", se=F)+
  theme_bw()+
  scale_color_mpi()
```

